\chapter{Acknowledgment}

In this last chapter i would like firstly to thank you for reading this report. I hope that this was accurate enough and that this was constructing for you. For this internship I have to thank a lot of people that helped me through this adventure.\newline

\section{Internship's mentors}
With all the work i produced, i would also like to thank Mr.Chepoi and Mr.Vaxes my intership's mentors, who despite the current covid-19 situation helped me. 

With visio-conferences and mail exchanges they managed to keep me interested in research and especially in this subject matter. I cannot count the answers that they gave to the millions of questions that i had and always with a pedagogic approach.

Even though this internship's subject was hard they always pushed me to try and understand, search, and learn what i needed to know to move forward.

In this confinement circumstances, while home working I didn't felt alone at any time. When I had questions, my internship's mentor gave me enough information so that I could work by myself. The objective of this internship was to make me learn more about research, ho it is done and of course learn more about Pareto envelopes and Manhattan networks.\newline

I personally feel that i did even more than that, I had to learn how to read scientific publications, how to search information in a bibliography, how to retrieve from Internet publish articles, understand how do some data structures works without knowing them before. 

I had to prepare small talks for my visio-conferences with Mr.Vaxes and Mr.Chepoi, to explain what did I learn, what did I do, and what were my questions. I learned a lot on paper writing also.

\section{Making this internship possible}
Preparing all of the required papers for an internship is compulsory and a long work. And I cannot end this paper without showing how much grateful I am to three particular persons.

Especially in the current sanitation situation, retrieving all the needed papers, and all needed signatures was not a soft task to do. Alone i would never have been able to do so.\newline

For this I have to gratefully thank Mme.JAMET and Mme.JEANSON whom helped me a lot with the paperwork for the University side.I took some time to understand what was wanted from me. But after starting the procedures, and mails after mails Mme.JEANSON and Mme.JAMET always answered me with astonishing rapidity and accurate instructions. And for this thank again.

For the laboratory side, I need to thank Mmme.COMES, my interlocutor for the LIS. She also help me to summaries and centralize all of my papers while starting this internship.

The current situation was not really usual but even in hard times Mme.JAMET, Mme.JEANSON and Mme.Comes helped me in making this internship possible. Nothing of this was going to be real and possible if they were not here.